An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/rel.tex
more corrections

Providing language support has been considered a promising way  
to tackle configuration problems~\cite{xu15systems}.
Nevertheless, a practical language-based misconfiguration
detection approach still remains an open problem.

\para{Configuration languages.}
There have been several language-support efforts proposed for preventing
configuration errors introduced by fundamental deficiencies in
either untyped or low-level languages. For example, in the network
configuration management area, it is easy for administrators to
produce configuration errors in their routing configuration files.
PRESTO~\cite{enck07configuration} 
automates the generation of device-native configurations
with configlets in a template language. 
Loo {\em et al.}~\cite{loo05declarative} adopt Datalog to reason about 
routing protocols in a declarative fashion. 
COOLAID~\cite{chen10declarative} constructs
a language to describe domain knowledge about network devices and
services to convenient network reasoning and management.

@@

\para{Misconfiguration detection.}
Misconfiguration detection techniques aim at checking the configuration
efforts before the system outages occur.
Most of existing detection approaches check 
the configuration files against a set of predefined correctness 
rules, named constraints, and then report the errors if 
the checked configuration files do not satisfy these rules.

@@

Several machine learning-based misconfiguration detection efforts 
also have been proposed~\cite{yuan11context, zhang14encore}.
EnCore~\cite{zhang14encore} is the most close work to \app.
It introduces a template-based
learning approach to improve the accuracy of their learning results.
The learning process is guided by a set of predefined rule templates
that enforce learning to focus on patterns of interests.
By this way, EnCore filters out irrelevant information and reduces
the false positives; moreover, the templates are able to express
system environment information that other machine learning
techniques cannot handle.
Compared with EnCore, \app has the following advantages.
First, \app does not rely on whether the files in given configuration set 
are 100\% correct. Second, \app not only can cover much more types of 
misconfigurations, but also introduces probabilistic type.
Finally, \app is a language framework, which could 
even be used to write configuration files, but EnCore is only a 
misconfiguration detection tool.

\para{Misconfiguration diagnosis.}
Many misconfiguration diagnosis approaches have been proposed%
~\cite{attariyan10automating, attariyan12x-ray}.
For example, ConfAid~\cite{attariyan10automating} 
and X-ray~\cite{attariyan12x-ray} use dynamic information
flow tracking to find possible configuration errors that may result in
failures or performance problems. AutoBash~\cite{su07autobash} 
speculatively
executes processes and tracks causality to automatically fix 
misconfigurations. Different from \app, most of misconfiguration
diagnosis efforts aim at finding out errors after the system
failures occur, which typically lead to prolonged recover time.

>>>>

Language support has been considered a promising way  
to tackle configuration problems~\cite{xu15systems}.
Nevertheless, a practical language-based misconfiguration
detection approach still remains an open problem.

\para{Configuration languages.}
There have been several language-support efforts proposed for preventing
configuration errors introduced by fundamental deficiencies in
either untyped or low-level languages. For example, in the network
configuration management area, it is easy for administrators to
produce configuration errors in their routing configuration files.
PRESTO~\cite{enck07configuration} 
automates the generation of device-native configurations
with configlets in a template language. 
Loo {\em et al.}~\cite{loo05declarative} adopt Datalog to reason about 
routing protocols in a declarative fashion. 
COOLAID~\cite{chen10declarative} constructs
a language to describe domain knowledge about devices and
services for convenient network reasoning and management.

@@

\para{Misconfiguration detection.}
Misconfiguration detection techniques aim at checking configuration
efforts before system outages occur.
Most existing detection approaches check 
the configuration files against a set of predefined correctness 
rules, named constraints, and then report errors if 
the checked configuration files do not satisfy these rules.

@@

Several machine learning-based misconfiguration detection efforts 
also have been proposed~\cite{yuan11context, zhang14encore}.
EnCore~\cite{zhang14encore} is the work closest to \app.
It introduces a template-based
learning approach to improve the accuracy of their learning results.
The learning process is guided by a set of predefined rule templates
that enforce learning to focus on patterns of interest.
In this way, EnCore filters out irrelevant information and reduces
false positives; moreover, the templates are able to express
system environment information that other machine learning
techniques cannot handle.
Compared to EnCore, \app has the following advantages.
Firstly, \app does not rely on 100\% correctness in the files of the given configuration set. 
Secondly, \app not only can cover much more types of 
misconfigurations, but also introduces probabilistic type.
Finally, \app is a language framework, which could 
even be used to write configuration files, but EnCore is only a 
misconfiguration detection tool.

\para{Misconfiguration diagnosis.}
Many misconfiguration diagnosis approaches have been proposed%
~\cite{attariyan10automating, attariyan12x-ray}.
For example, ConfAid~\cite{attariyan10automating} 
and X-ray~\cite{attariyan12x-ray} use dynamic information
flow tracking to find possible configuration errors that may result in
failures or performance problems. AutoBash~\cite{su07autobash} 
speculatively
executes processes and tracks causality to automatically fix 
eisconfigurations. Different from \app, most of misconfiguration
diagnosis efforts aim at finding out errors after the system
failures occur, which typically lead to prolonged recover time.
